# RESULTS

## FISHING OPERATIONS
```{r fishing}

coastaltows <- nrow(bridgetow)

coastalhigh <- bridgetow %>%
  pull(`Net Opening Height (m)`) %>%
  mean %>%
  round()

coastalwide <- bridgetow %>%
  pull(`Net Opening Width (m)`) %>%
  mean %>%
  round()

```

This survey completed `r coastaltows` coastal LFS 7742 trawl net tows (Appendix \@ref(app:appBridge)). The coastal LFS 7742 trawl net averaged `r coastalhigh` m high by `r coastalwide` m wide, or an area of `r round(coastalhigh * coastalwide)` m^2^, during tows on this survey. This mouth area is larger than originally designed (15 m x 30 m), but similar to a previous survey on the *FV Sea Crest* where the coastal LFS 7742 trawl net mouth opening averaged 19 m high by 41 m wide at the surface, or area of 779 m^2^, and 13 m high by 47 m wide at a headrope depth of 15 m, or area of 611 m^2^ [@anderson2019]. All catch per unit effort (CPUE) reported here are standardized by swept volume to standardize catch values.

## CATCH COMPOSITION
```{r catchcomposition}

totalcatchkg <- round(sum(catch$totalWgt, na.rm = TRUE)/1000)

totalsalmon <- catch %>%
  filter(str_extract(SCIENTIFIC_NAME, "Oncorhynchus") == "Oncorhynchus")

totalsalmonkg <- round(sum(totalsalmon$totalWgt, na.rm = TRUE)/1000)

percentsalmon <- round(totalsalmonkg/totalcatchkg*100)

numSpecies <- nrow(catch)

abundantspeciesnames1 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  first

abundantspeciesnames1kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames1) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames2 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames2kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames2) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames3 <- catch %>%
  slice(3:3) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames3kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames3) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

salmonByWt <- catch %>%
  filter(str_detect(COMMON_NAME, "Salmon")) %>%
  arrange(-totalWgt) %>%
  pull(COMMON_NAME)

salmonByWtCommas <- paste0(str_trim(salmonByWt), collapse = ", ")

```

For each of `r numSpecies` species captured during the survey, the number of tows in which the species was present, total catch weight, maximum catch weight, and mean catch weight per tow for usable tows is presented in Table \@ref(tab:catchtable). The most abundance species caught by weight were `r abundantspeciesnames1`, primarily caught in one set (`r abundantspeciesnames1kg` kg), `r abundantspeciesnames2` (`r abundantspeciesnames2kg` kg), then `r abundantspeciesnames3` (`r abundantspeciesnames3kg` kg; Table \@ref(tab:catchtable)). All species of juvenile Pacific Salmon were caught. The order of abundance by weight was: `r salmonByWtCommas`. Total catch for the survey from usable tows was `r totalcatchkg` kg, with `r totalsalmonkg` kg or `r percentsalmon`% Pacific Salmon. Detailed catch composition for each tow is included in Appendix \@ref(app:appCatch).

Pink Salmon had the highest abundance by count and were most abundant from Johnstone Strait to Queen Charlotte Strait (Figure \@ref(fig:pkcpue)). Chum Salmon were second most abundant by count, with the highest catches within Queen Charlotte Strait, the entrance to Rivers Inlet, and beside Thurlow Islands (Figure \@ref(fig:cmcpue)). Chinook Salmon were abundant in Wells Passage and southern Johnstone Strait (Figure \@ref(fig:ckcpue)). Juvenile Sockeye Salmon were abundant at the border of Johnstone Strait and Queen Charlotte Strait and one tow within Queen Charlotte Sound (Figure \@ref(fig:secpue)). Finally, Coho Salmon were the least abundant salmon species with only 30 individuals caught, mainly in Queen Charlotte Strait and the entrance to Rivers Inlet (Figure \@ref(fig:cocpue)). 

## BIOLOGICAL SAMPLES

Samples were collected for DNA stock composition (`r numDNA`), otoliths (`r numOtoliths`), energy density (`r numWholebodies`), stable isotope analysis (`r numMuscles`), and coded wire tags (`r numCTW`). These biological samples are located at the Pacific Biological Station, Fisheries and Oceans Canada (Nanaimo, BC).

## LENGTH AND WEIGHT
```{r lengthandweight}

lwspeciesnum <- nrow(lw)

lwsalmon <- lw %>%
  filter(str_extract(COMMON_NAME, "Salmon") == "Salmon")

bigsalmon <- lwsalmon %>%
  arrange(-meanLen) %>%
  slice(1:1)

bigsalmonNam <- bigsalmon %>% pull(COMMON_NAME)
bigsalmonLen <- bigsalmon %>% pull(meanLen)
bigsalmonWGT <- bigsalmon %>% pull(meanWGT)

smlsalmon <- lwsalmon %>%
  arrange(meanLen) %>%
  slice(1:1)

smlsalmonNam <- str_to_title(smlsalmon %>% pull(COMMON_NAME))
smlsalmonLen <- smlsalmon %>% pull(meanLen)
smlsalmonWGT <- smlsalmon %>% pull(meanWGT)

```

Length frequencies and length-weight relationships are presented for juvenile Pacific Salmon species in Figures \@ref(fig:forkcm) to \@ref(fig:forkco). Double log transformed length-weight regressions coefficients were similar for three of the five Pacific Salmon species (Pink Salmon, Chum Salmon, Chinook Salmon). Sockeye Salmon and Coho Salmon had smaller slopes compared to the other Pacific Salmon species (Figures \@ref(fig:forkse) and \@ref(fig:forkco)). Mean, minimum, and maximum lengths and weights of `r lwspeciesnum` species were recorded, with all five Pacific Salmon species represented (Table \@ref(tab:lwtable)), Juvenile `r bigsalmonNam` had the largest mean length (`r bigsalmonLen` mm) and weight (`r bigsalmonWGT` g), whereas juvenile `r smlsalmonNam` had the smallest mean length (`r smlsalmonLen` mm) and weight (`r smlsalmonWGT` g) of the Pacific Salmon species. These size differences are expected given the different life histories of Pacific Salmon species. For example, juvenile Sockeye Salmon may migrate to the marine environment in their first year, whereas juvenile Coho Salmon migrate later and some individuals remain in the coastal environment [@quinn2018].

## STOMACH CONTENTS
```{r stomachcontents}

totalstomachs <- sum(stomachdf$NumStomachs)
totalstomachspecies <- nrow(stomachdf)

salmonstomachs <- stomachdf %>%
  filter(str_extract(COMMON_NAME, "Salmon") == "Salmon") %>%
  arrange(-PerEmpty)

ckstomach <- stomachdf %>%
  filter(COMMON_NAME == "Chinook Salmon") %>%
  pull(PerEmpty)

costomach <- stomachdf %>%
  filter(COMMON_NAME == "Coho Salmon") %>%
  pull(PerEmpty)

cmstomach <- stomachdf %>%
  filter(COMMON_NAME == "Chum Salmon") %>%
  pull(PerEmpty)

pkstomach <- stomachdf %>%
  filter(COMMON_NAME == "Pink Salmon") %>%
  pull(PerEmpty)

sestomach <- stomachdf %>%
  filter(COMMON_NAME == "Sockeye Salmon") %>%
  pull(PerEmpty)

```

Stomachs of `r totalstomachs` individual fish, from `r totalstomachspecies` species, were analysed at sea (Table \@ref(tab:stomachtable)). Chinook Salmon (`r ckstomach`%) had the highest percentage of empty stomachs, whereas Chum Salmon (`r cmstomach`%) had the lowest percentage of empty stomach within Pacific Salmon species. Pink Salmon (`r pkstomach`%), Sockeye Salmon (`r sestomach`%), and Coho Salmon (`r costomach`%) had comparable percentages of empty stomachs (Table \@ref(tab:stomachtable)).  

Juvenile Pacific Salmon showed species-specific differences in their prey items (Table \@ref(tab:preytable)). The most common prey within juvenile Pink Salmon, Sockeye Salmon, and Coho Salmon stomachs were amphipods and euphausiids. Juvenile Chum Salmon also preyed upon amphipods and euphausiids; however, juvenile chum had more unidentified remains within their stomachs. Jellyfish and Squid are digested quickly; therefore, unidentified remains may represents those prey species. Juvenile Chinook salmon were primarily eating Pacific Herring and amphipods by count, although two individuals had a large volume of squid of their stomachs (Table \@ref(tab:preytable)). 

## OCEANOGRAPHY
```{r oceanography}

ctdmaxdepth <- max(ctd_orig$CTD_DEPTH)
ctdmindepth <- min(ctd_orig$CTD_DEPTH)
  
```

CTD casts and water samples were completed at `r nrow(ctd_orig)` sites with cast depths ranging from `r ctdmindepth` m to `r ctdmaxdepth` m (Appendix \@ref(app:appOcean)). Samples were collected for nutrients and chlorophyll at approximately 10 m from the surface. Oceanographic data from the CTD casts and nutrient analysis of the water samples are archived online within the [Water Properties Data Inventory](https://www.waterproperties.ca) under cruise number 2019-125 as well as [Canadian Inegrated Ocean Observing System](https://cioos.ca/) or CIOOS. 

## ZOOPLANKTON
```{r planktonresults}

planktonvert <- plankton_orig %>%
  mutate(BONGO_DEPTH = if_else(is.na(RBR_DEPTH), TARGET_DEPTH, RBR_DEPTH))

planktonmax <- max(planktonvert$BONGO_DEPTH)
planktonmin <- min(planktonvert$BONGO_DEPTH)

```

Vertical bongo tows were conducted at `r nrow(planktonvert)` stations to depths ranging from `r planktonmin` m to `r planktonmax` m (Appendix \@ref(app:appOcean)). Formalin-preserved zooplankton samples will be identified and enumerated at the Institute of Ocean Sciences, Fisheries and Oceans Canada (Sidney, BC). Data will be archived in the zooplankton database. Fractionated zooplankton samples are frozen at the Pacific Biological Station, Fisheries and Oceans Canada (Nanaimo, BC).

## ACOUSTIC DATA
Acoustic data was collected throughout the survey for analysis at the Institute of Ocean Sciences, Fisheries and Oceans Canada (Sidney, BC).
