# RESULTS

## FISHING OPERATIONS
```{r fishing}

coastaltows <- nrow(bridgetow)

coastalhigh <- bridgetow %>%
  pull(`Net Opening Height (m)`) %>%
  mean %>%
  round()

coastalwide <- bridgetow %>%
  pull(`Net Opening Width (m)`) %>%
  mean %>%
  round()

```

This survey completed `r coastaltows` coastal LFS 7742 trawl net tows (Appendix \@ref(app:appBridge)). The coastal LFS 7742 trawl net averaged `r coastalhigh` m high by `r coastalwide` m wide, or an area of `r round(coastalhigh * coastalwide)` m^2^, during surface tows on this survey. This mouth area is similar to a previous survey on the *FV Sea Crest* where the coastal LFS 7742 trawl net mouth opening averaged 19 m high by 41 m wide at the surface, or area of (779 m^2^; [@anderson2019]). All catch per unit effort (CPUE) reported here are standardized by swept volume to standardize catch values.

## CATCH COMPOSITION
```{r catchcomposition}

totalcatchkg <- round(sum(catch$totalWgt, na.rm = TRUE)/1000)

totalsalmon <- catch %>%
  filter(str_extract(SCIENTIFIC_NAME, "Oncorhynchus") == "Oncorhynchus")

totalsalmonkg <- round(sum(totalsalmon$totalWgt, na.rm = TRUE)/1000)

percentsalmon <- round(totalsalmonkg/totalcatchkg*100)

numSpecies <- nrow(catch)

abundantspeciesnames1 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  first

abundantspeciesnames1kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames1) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames2 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames2kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames2) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames3 <- catch %>%
  slice(3:3) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames3kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames3) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

salmonByWt <- catch %>%
  filter(str_detect(COMMON_NAME, "Salmon")) %>%
  arrange(-totalWgt) %>%
  pull(COMMON_NAME)

salmonByWtCommas <- paste0(str_trim(salmonByWt), collapse = ", ")

```

For each of `r numSpecies` species captured during the survey, the number of tows in which the species was present, total catch weight, maximum catch weight, and mean catch weight per tow for usable tows is presented in Table \@ref(tab:catchtable). The most abundance species caught by weight were `r abundantspeciesnames1`, primarily caught in one set (`r abundantspeciesnames1kg` kg), `r abundantspeciesnames2` (`r abundantspeciesnames2kg` kg), then `r abundantspeciesnames3` (`r abundantspeciesnames3kg` kg; Table \@ref(tab:catchtable)). All species of juvenile Pacific Salmon were caught. The order of abundance by weight was: `r salmonByWtCommas`. Total catch for the survey from usable tows was `r totalcatchkg` kg, with `r totalsalmonkg` kg or `r percentsalmon`% Pacific Salmon. Detailed catch composition for each tow is included in Appendix \@ref(app:appCatch).

Pink Salmon had the highest abundance by count and were most abundant from Johnstone Strait to Queen Charlotte Strait (Figure \@ref(fig:pkcpue)). Chum Salmon were second most abundant by count, with the highest catches within Queen Charlotte Strait, the entrance to Rivers Inlet, and beside Thurlow Islands (Figure \@ref(fig:cmcpue)). Chinook Salmon were abundant in Wells Passage and southern Johnstone Strait (Figure \@ref(fig:ckcpue). Juvenile Sockeye Salmon were abundant at the border of Johnstone Strait and Queen Charlotte Strait and one tow within Queen Charlotte Sound (Figure \@ref(fig:secpue)). Finally, Coho Salmon were the least abundant salmon species with only 30 individuals, mainly caught in Queen Charlotte Strait and the entrance to Rivers Inlet (Figure \@ref(fig:cocpue)). 

## BIOLOGICAL SAMPLES
```{r lengthandweight}

lwspeciesnum <- nrow(lw)

lwsalmon <- lw %>%
  filter(str_extract(COMMON_NAME, "Salmon") == "Salmon")

bigsalmon <- lwsalmon %>%
  arrange(-meanLen) %>%
  slice(1:1)

bigsalmonNam <- bigsalmon %>% pull(COMMON_NAME)
bigsalmonLen <- bigsalmon %>% pull(meanLen)
bigsalmonWGT <- bigsalmon %>% pull(meanWGT)

smlsalmon <- lwsalmon %>%
  arrange(meanLen) %>%
  slice(1:1)

smlsalmonNam <- str_to_title(smlsalmon %>% pull(COMMON_NAME))
smlsalmonLen <- smlsalmon %>% pull(meanLen)
smlsalmonWGT <- smlsalmon %>% pull(meanWGT)

```

Length frequencies and length-weight relationships are presented for juvenile Pacific Salmon species in Figures \@ref(fig:forkpk) to \@ref(fig:forkco). Double log transformed length-weight regressions coefficients were similar for three of the five Pacific Salmon species. Sockeye Salmon and Coho Salmon had lower a smaller slope compared to the other Pacific Salmon species (Figures \@ref(fig:forkco) and \@ref(fig:forkco)). Lengths and weights of `r lwspeciesnum` species were recorded, with all five Pacific Salmon species represented (Table \@ref(tab:lwtable)) `r bigsalmonNam` had the largest mean length (`r bigsalmonLen` mm) and weight (`r bigsalmonWGT` g), whereas `r smlsalmonNam` had the smallest mean length (`r smlsalmonLen` mm) and weight (`r smlsalmonWGT` g) of the Pacific Salmon species. These size differences are expected given the different life histories of Pacific Salmon species. For example, juvenile Sockeye Salmon may migrate to the marine environment in their first year, whereas juvenile Coho Salmon migrate later and some individuals remain in the coastal environment [@quinn2018].

## LENGTH AND WEIGHT

## STOMACH CONTENTS

## OCEANOGRAPHY

## ZOOPLANKTON

## ACOUSTIC DATA