# FIGURES

(ref:mapfish) Fishing tow locations during the `r surveyName` from `r surveyDateRange` on the *`r vessel`*. The target head rope depth was 0 m (orange circles) or 15 m (red triangles). 

```{r mapfish, fig.pos="H", fig.cap = "(ref:mapfish)", warning=FALSE}

  basemap +
    geom_point(data = tows,
      aes(START_LONG, START_LAT, shape = TARGET_DEPTH, color = TARGET_DEPTH),
             size = 3) +
    scale_color_manual(values = c("orange", "darkred")) +
  labs(shape = "Depth", color = "Depth")


```

(ref:mapctd) Oceanographic and zooplankton sampling locations during the `r surveyName` from `r surveyDateRange` on the *`r vessel`*. There were ?? Seabird 25 CTD casts (red circles) and ?? zooplankton vertical tows (orange triangles).

```{r mapctd, fig.pos="H", fig.cap = "(ref:mapctd)", warning=FALSE}

events_ctd <- events %>%
  filter(Type == "ROS" | Type == "CTD")
  
  basemap +
    geom_point(data = events_ctd,
             aes(Start_Long_DD, Start_Lat_DD, shape = Type, color = Type),
             size = 3) +
    scale_color_manual(values = c("darkred", "orange")) +
    theme(legend.position = "none")
  

```

\FloatBarrier
\newpage