# FIGURES

(ref:mapfish) Fishing tow locations during the `r surveyName` from `r surveyDateRange` on the *`r vessel`*. The target head rope depth was 0 m (orange circles) or 15 m (red triangles). 

```{r mapfish, fig.pos="H", fig.cap = "(ref:mapfish)", warning=FALSE}

  basemap +
    geom_point(data = tows,
      aes(START_LONG, START_LAT, shape = TARGET_DEPTH, color = TARGET_DEPTH),
             size = 3) +
    scale_color_manual(values = c("orange", "darkred")) +
  labs(shape = "Depth", color = "Depth")


```

(ref:mapctd) Oceanographic and zooplankton sampling locations during the `r surveyName` from `r surveyDateRange` on the *`r vessel`*. There were `r nrow(ctd_simp)` Seabird 25 CTD casts and `r nrow(plankton_simp)` zooplankton vertical tows.

```{r mapctd, fig.pos="H", fig.cap = "(ref:mapctd)", warning=FALSE}

# on survey 2019-125 both event happened at every location
# therefore no need to show both
  basemap +
    geom_point(data = ctd_simp,
      aes(LONG, LAT),
             size = 3, color = "darkred")

  

```

\FloatBarrier
\newpage